Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-08 prob.tex
Updates from ShareLaTeX
prob.tex \section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued Probability Measures} Updated...

Although example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
rely on $\imposs$ to deduce that an interval-valued probability measure
has an empty core, it is not necessary. The following example is modified
from example~\ref{ex:three-dimensional-4-value}, but has the property
that $\bar{\mu}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.

\begin{example}[Another three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value-2} Consider\emph{
}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
and $\ket{0}$, $\ket{1}$, $\ket{2}$, $\ket{\ps}$, $\ket{\ms}$,
and $\bar{\mu}$ are defined as in example~\ref{ex:three-dimensional-4-value}
except 
\begin{eqnarray*}
\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \unlikely\\
\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \likely\textrm{ .}
\end{eqnarray*}
By following the same as process as in example~\ref{ex:three-dimensional-4-value},
it is easy to verify that $\bar{\mu}$ is an interval-valued probability
measure.

We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\likely$
implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge\frac{1}{2}$.
On the other hand, by figure~\ref{fig:three-dimensional-4-value},
it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\unlikely$,
i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le\frac{1}{2}$. Because
$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.
Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=\frac{1}{2}$.

Consider a general density matrix~ $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{2}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{2}}r_{ij}\ket{i}\bra{j}$.
Then, we have
\begin{eqnarray*}
\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta\ket{i}+r_{i2}\cos\theta\ket{i}\right)\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
\end{eqnarray*}
Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.\qed\end{example}
\end{document}

>>>>

Although it is easier to deduce an interval-valued probability measure
has an empty core by considering the state mapped to $\imposs$ as
in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
it is not the only way to prove an interval-valued probability measure
has an empty core. The following family of interval-valued probability
measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
if $P=\mathbb{0}$, but we can still prove them have empty cores.

\begin{example}[Another three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value-2} Given
$r_{0}\in\left[\frac{1}{3},\frac{1}{2}\right]$, we are going to construct
an interval-valued probability measures for each $r_{0}$, and it
has an empty core whenever $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.

Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\necess,\left[1-2r_{0},r_{0}\right],\left[1-r_{0},2r_{0}\right],\left[2-4r_{0},1-r_{0}\right],\left[r_{0},4r_{0}-1\right]\right\} $.
This is well-defined since the left-end is less or equal to the right-end
whenever $r_{0}\ge\frac{1}{3}$. If $\ket{0}$, $\ket{1}$, $\ket{2}$,
$\ket{\ps}$, $\ket{\ms}$, $\ket{0_{\theta,\gamma}^{\perp}}$, and
$\ket{\ps_{\theta,\gamma}^{\perp}}$ are defined as in example~\ref{ex:three-dimensional-4-value},
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
can be defined as follow: 
\begin{enumerate}
\item $\bar{\mu}(\mathbb{0})=\imposs$ and $\bar{\mu}(\mathbb{1})=\necess.$
\item For the dotted half of the red and green circles in figure~\ref{fig:three-dimensional-4-value},
i.e., whenever $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$,
we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[r_{0},4r_{0}-1\right]\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \left[2-4r_{0},1-r_{0}\right]\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\left[1-2r_{0},r_{0}\right]$ and
$\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\left[1-r_{0},2r_{0}\right]$. 
\end{enumerate}
We now prove $\bar{\mu}$ has an empty core by contradiction. Assume
there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. We first claim that for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
On one hand, $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\in\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\left[r_{0},4r_{0}-1\right]$
implies $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\ge r_{0}$.
On the other hand, by figure~\ref{fig:three-dimensional-4-value},
it is easy to see for any neighborhood of $\ket{0_{\theta,\gamma}^{\perp}}$,
these is always a state~$\ket{\psi}$ such that $\mu_{\rho}^{B}\left(\proj{\psi}\right)\in\bar{\mu}\left(\proj{\psi}\right)=\left[1-2r_{0},r_{0}\right]$,
i.e., $\mu_{\rho}^{B}\left(\proj{\psi}\right)\le r_{0}$. Because
$\mu_{\rho}^{B}$ is continuous, we have $\mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=r_{0}$.
Similarly, $\mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)=r_{0}$.

Consider a general density matrix~ $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{2}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{2}}r_{ij}\ket{i}\bra{j}$.
\begin{eqnarray*}
r_{0} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta+r_{i2}\cos\theta\right)\ket{i}\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
\end{eqnarray*}
Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=r_{0}$.
We also have
\begin{eqnarray*}
r_{0} & = & \mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(-\frac{r_{i0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{i1}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{i2}\cos\theta\right)\ket{i}\left(-\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{0}+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & -\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{00}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{01}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{02}\cos\theta\right)\\
 &  & +\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{10}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}\right)+\cos\theta\left(-\frac{r_{20}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{0}\cos\theta\right)\\
 & = & \left(\frac{r_{00}\sin^{2}\theta}{2}-\frac{r_{01}\sin^{2}\theta}{2}-\frac{r_{02}\rme^{-\rmi\gamma}\sin\theta\cos\theta}{\sqrt{2}}\right)+\left(-\frac{r_{10}\sin^{2}\theta}{2}+\frac{r_{0}\sin^{2}\theta}{2}\right)+\left(-\frac{r_{20}\rme^{\rmi\gamma}\cos\theta\sin\theta}{\sqrt{2}}+r_{0}\cos^{2}\theta\right)\\
 & = & \left(\frac{r_{00}}{2}-\frac{r_{01}}{2}-\frac{r_{10}}{2}+\frac{r_{0}}{2}\right)\sin^{2}\theta+r_{0}\cos^{2}\theta-\left(r_{02}\rme^{-\rmi\gamma}+r_{20}\rme^{\rmi\gamma}\right)\frac{\cos\theta\sin\theta}{\sqrt{2}}
\end{eqnarray*}
Because of the same reason, we have $r_{02}=r_{20}=0$ and $r_{00}=r_{0}+r_{01}+r_{10}$.
Moreover, because $\rho$ is a density matrix, we should have $\rho^{\dagger}=\rho$,
$\Tr\left(\rho\right)=1$, and $\rho$ is a positive operator~\cite{544199}.
These implies that we can express $r_{01}=a+\rmi b$ and $r_{10}=a-\rmi b$
for some $a$, $b\in\mathbb{R}$. After plugging into $\Tr\left(\rho\right)=1$,
we have $r_{00}=1-2r_{0}$, $r_{01}=\frac{1}{2}-\frac{3}{2}r_{0}+\rmi b$,
and $r_{01}=\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b$. Next, since $\rho$
is a positive operator, $\rho$ should have all non-negative eigenvalues,
which are the solutions of the characteristic polynomial
\begin{eqnarray*}
0 & = & \det\left(\rho-\lambda\mathbb{1}\right)\\
 & = & \begin{vmatrix}1-2r_{0}-\lambda & \frac{1}{2}-\frac{3}{2}r_{0}+\rmi b & 0\\
\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b & r_{0}-\lambda & 0\\
0 & 0 & r_{0}-\lambda
\end{vmatrix}\\
 & = & \left(r_{0}-\lambda\right)\left[\left(1-2r_{0}-\lambda\right)\left(r_{0}-\lambda\right)-\left(\frac{1}{2}-\frac{3}{2}r_{0}+\rmi b\right)\left(\frac{1}{2}-\frac{3}{2}r_{0}-\rmi b\right)\right]\\
 & = & \left(r_{0}-\lambda\right)\left[\lambda^{2}-\left(1-r_{0}\right)\lambda+r_{0}-2r_{0}^{2}-\frac{1}{4}+\frac{3}{2}r_{0}-\frac{9}{4}r_{0}^{2}-b^{2}\right]\\
 & = & \left(r_{0}-\lambda\right)\left[\lambda^{2}-\left(1-r_{0}\right)\lambda-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right]
\end{eqnarray*}
Hence, the solutions of $\lambda$ are $r_{0}$ and $1-r_{0}\pm\sqrt{\left(1-r_{0}\right)^{2}-4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)}$.
If they are all non-negative, we want 
\begin{eqnarray*}
0 & \ge & -4\cdot1\cdot\left(-\frac{1}{4}+\frac{5}{2}r_{0}-\frac{17}{4}r_{0}^{2}-b^{2}\right)\\
 & = & 1-10r_{0}+17r_{0}^{2}+4b^{2}\\
 & = & 17\left(r_{0}-\frac{5+\sqrt{25-17\cdot\left(4b^{2}+1\right)}}{17}\right)\left(r_{0}-\frac{5-\sqrt{25-17\cdot\left(4b^{2}+1\right)}}{17}\right)
\end{eqnarray*}
Therefore, when $r_{0}>\frac{5+2\sqrt{2}}{17}$ or $r_{0}<\frac{5-2\sqrt{2}}{17}$,
no matter which $b\in\mathbb{R}$, $\rho$ always has a negative eigenvalue.
This contradiction implies $\bar{\mu}$ has an empty core when $r_{0}\in\left(\frac{5+2\sqrt{2}}{17},\frac{1}{2}\right]$.\qed\end{example}

\end{document}
